Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-03 yfcc100m/paper/vldb2020/intro.tex
Update intro and other minor changes

Visual computing workloads performing analytics on
video or image data, either off-line or streaming,
have become prolific across a wide range of application domains.
This is in part due to the growing ability of machine learning techniques to
extract information out of the visual data which can subsequently be used
for informed decision making.
The insights this information can provide depend on the
application: a retail vendor might be interested in the amount of time
shoppers spend in front of a specific product, while a medical expert might
want to see the effect of a specific treatment on the size of a tumor.

>>>>

Visual computing workloads performing analytics on
video or image data, either off-line or streaming,
have become prolific across a wide range of application domains.
This is in part due to the growing ability of machine learning techniques to
extract information out of the visual data which can subsequently be used
for informed decision making \cite{vdms-nips}.
The insights this information can provide depend on the
application: a retail vendor might be interested in the amount of time
shoppers spend in front of a specific product, while a medical expert might
want to see the effect of a specific treatment on the size of a tumor.

There are many applications that can be studied through the use of large
and public available datasets. But before getting started, there is usually
a large effort devoted to cleaning up the data. For this work, we use
the YFCC100m dataset as an example given that we have use the same dataset
for multiple proof of concepts and applications without our research lab.
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine generated tags for each image, and video summarization.
In all cases, it was needed to select a subset of the data before running
any processing. Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searched
based on tags (relational database, graph database, csv files, etc), and
building the necessary pipelines for querying and retrieving the right data.

Data scientist and machine learning developers usually end up building ad-hoc
solutions through a combination of databases and file systems to store metadata
and visual data (images, videos), respectively.
